Low-Cost Data Deduplication for Virtual Machine Backup in Cloud Storage

### 2013-07-26 batchdedup/eval.tex
Added initial memory comparison figures

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 100 
Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE} and each
of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

@@

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
limit $M$ imposed on each node varies.
%  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
and final data copying to the backup storage is overlapped with VM scanning.
During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 95MB.
The aggregated deduplication throughput is  about 8.76GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 3.1 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.

>>>>

%We are running our deduplication/backup  service on 100 nodes.
%Memory usage is about 150MB space per node during backup and
%the CPU usage is very small during the experiments. 
We have performed a trace-driven study using  a 1323 VM dataset  collected from 
%100 Alibaba Aliyun's cloud nodes~\cite{WeiZhangIEEE}.
a cloud cluster at Alibaba's Aliyun.
% ~\cite{WeiZhangIEEE}.
% and each of machine nodes has 16 cores and 12 disk drives,  hosting  up to 25 VMs. 
For each VM, the system keeps 10 automatically-backed snapshots in the storage while
a user may instruct extra snapshots to be saved.
The backup of VM snapshots is completed within a few  hours every night.
Based on our study of its production  data,  each VM has about  40GB of storage  data usage on average
including OS and user data disk.
Each VM image is  divided into 2 MB fix-sized segments and each segment is divided into 
variable-sized content blocks  with an average size of 4KB.
%variable sizes~\cite{similar94,rabin81} with an average size of 4KB. 
The signature for variable-sized blocks is computed using their SHA-1 hash.

@@

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Network Buffer Size},
		xlabel={Total Network Memory Buffer (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=mpibufmem,y=totaltime] {figures/mpibufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, write buffer 6.25MB, Read Buffer 128KB}
  \label{fig:mpibuf-mem}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Read Buffer Size},
		xlabel={Read Buffer Size (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=rbufmem,y=totaltime] {figures/rbufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to disk read buffering. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffers 2.5MB, write buffer 6.25MB}
  \label{fig:mpibuf-mem}
\end{figure}

\begin{figure}[ht]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
		%title={Write Buffer Size},
		xlabel={Total Write Buffer Memory (MB)},
		ylabel={Backup Time},
		%extra y ticks={4.5,5.5,6.5} %to show extra ticks
		%legend pos=north west
		]
                \addplot table[x=wbufmem,y=totaltime] {figures/wbufmem.txt};
                %\legend{Total Backup Time};
		\end{axis}
	\end{tikzpicture}
  \caption{Backup time for verying amounts of memory allocated to network communication. Other Settings: 10 Machines, 5x40GB VMs per machine, network buffer memory 2.5MB, Read Buffer 128KB}
  \label{fig:mpibuf-mem}
\end{figure}

Figure~\ref{fig:memory} shows the total parallel time in hours to backup 2500 VMs on
 a 100-node cluster a  when 
limit $M$ imposed on each node varies.
%  from 20MB to 200MB.
This figure also depicts the time breakdown for Stages 1, 2, and 3. 
%The parallel time includes the first scanning time, 
%of dirty VM segments to generate block fingerprints, data redistribution for request accumulation,
%fingerprint comparison, duplicate summary distribution, and the second scan time for real backup.
The time in Stages 1 and 3  is  dominated by  the two scans of dirty segments,
and final data copying to the backup storage is overlapped with VM scanning.
During dirty segment reading, the average number of consecutive dirty segments is 2.92. 
%Each scan takes about 1.4 hours.
The overall processing time does not have a significant reduction as $M$ increases to 190MB.
The aggregated deduplication throughput is  about 8.76GB per second,
which is the size of 2500 VM images divided by the parallel time. 
The system runs with  a single thread and  its CPU resource usage is 10-13\% of one core. 
The result shows the backup with multi-stage deduplication  for all VM images can be 
completed in about 3.1 hours with 35MB memory,  8GB disk overhead and a small CPU usage.
As we vary the cluster size $p$,  the parallel time does  not change much, and  the aggregated throughput
scales up linearly since the number of VMs is  $25p$.

### 2013-07-26 batchdedup/main.tex
Added initial memory comparison figures

>>>>

\usepackage{pgfplots}
\pgfplotsset{compat=1.7}
\DeclareGraphicsExtensions{.pdf}

%pgfplots setup
\pgfplotsset{every axis/.append style={
	very thick,
	tick style={thick}}}
\pgfplotsset{
        every mark/.append style={solid}
}
\pgfplotscreateplotcyclelist{mcolor}{%
    {blue,every mark/.append style={fill=blue},mark=*},
    {red,every mark/.append style={fill=red},mark=square*},
    {brown,every mark/.append style={fill=brown},mark=triangle*,mark size=3},
    {black,every mark/.append style={fill=black},mark=diamond*,mark size=3},
    {green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3},
    {densely dashed,blue,every mark/.append style={fill=blue},mark=*},
    {densely dashed,red,every mark/.append style={fill=red},mark=square*},
    {densely dashed,brown,every mark/.append style={fill=brown},mark=triangle*,mark size=2.7},
    {densely dashed,black,every mark/.append style={fill=black},mark=diamond*,mark size=2.7},
    {densely dashed,green!60!black,every mark/.append style={fill=green!60!black},mark=pentagon*,mark size=2.5},
    {densely dashed,magenta!90!black,every mark/.append style={fill=magenta!90!black},mark=star,mark size=3}}

\pgfplotscreateplotcyclelist{mmark*}{
    {mark=*},
    {mark=square*},
    {mark=triangle*,mark size=2.7},
    {mark=diamond*,mark size=2.7},
    {mark=pentagon*,mark size=2.5},
    {mark=star,mark size=3},
    {mark=asterisk,mark size=3},
    {mark=+,mark size=3},
    {mark=Mercedes star,mark size=3}}

\pgfplotscreateplotcyclelist{mline}{
    {solid,blue,every mark/.append style={fill=blue}},
    {densely dashed,red,every mark/.append style={fill=red}},
    {densely dotted,brown,every mark/.append style={fill=brown}},
    {loosely dotted,black,every mark/.append style={fill=black}},
    {loosely dashed,green!60!black,every mark/.append style={fill=green!60!black}},
    {densely dashdotted,magenta!90!black,every mark/.append style={fill=magenta!90!black}},
    {densely dashdotdotted,teal,every mark/.append style={fill=teal}},
    {loosely dashdotted,orange,every mark/.append style={fill=orange}},
    {loosely dashdotdotted,violet,every mark/.append style={fill=violet}}}

    \pgfplotsset{cycle list name=mcolor}
